### 2020-07-28 draft.Rmd
Address Luke's feedback for sections 1 and 2

The two main outcomes of interest are 1. take-up of the commitment savings product and 2. savings at the financial institution. The authors use the baseline household survey to evaluate if there are any predictors to take-up. Savings balances at the institution, and not just in the commitment savings account, partially accounts for crowd-out to other savings vehicles.

The authors find that individuals open the accounts when offered. They also find that women are statistically significantly more likely to open accounts if they have hyperbolic preferences. They did not find a significant result for men. People have hyperbolic preferences if they exhibit a high discount rate in the immediate future and a lower discount rate further in the future. Accordingly, these individuals can improve their welfare with a commitment savings device.

The authors find that average savings increased by 81 percent for those in the treatment group relative to the control group after twelve months. The effect is significant at the $\alpha = 0.1$ level; however, the outcome variable is highly positively skewed.

@@

We find... todo(aaron): add a paragraph summarizing our conclusions

@@

```{r}
#
# Create a plot to show the skew of balchange
#
skewa = six_months %>%
  ggplot(aes(balchange)) +
  geom_density() +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(limits = c(0, 0.004)) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal()

@@

```{r}
seed_accounts = treated %>% 
  filter(treatment == 1)
nonseed = treated %>% 
  filter(treatment == 0)
hist(seed_accounts$balchange,
     main="Histogram of balance changes for SEED accounts",
     xlab="Balance Change")
filtered_seeds = seed_accounts %>% filter(balchange <=10000)
hist(filtered_seeds$balchange,
     main="Outliers removed balance changes for SEED accounts",
     xlab="Balance Change")
print("Summary statistics for Seed account balance changes")
summary(seed_accounts$balchange)
filtered_nonseeds = nonseed %>% filter(balchange<10000)
hist(nonseed$balchange)
hist(filtered_nonseeds$balchange)
```

>>>>

The two main outcomes of interest are 1. take-up of the commitment savings product and 2. savings at the financial institution. The authors use the baseline household survey to evaluate if there are any predictors to take-up. Savings balances at the institution, and not just in the commitment savings account, partially accounts for crowd-out to other savings vehicles. We focus exclusively on question 2.

For the first question, the authors find that individuals open the accounts when offered. They also find that women are statistically significantly more likely to open accounts if they have hyperbolic preferences. They did not find a significant result for men. People have hyperbolic preferences if they exhibit a high discount rate in the immediate future and a lower discount rate further in the future. Accordingly, these individuals can improve their welfare with a commitment savings device. We do not examine these results.

For the second question, the authors find that average savings increased by 81 percent for those in the treatment group relative to the control group after twelve months. The effect is significant at the $\alpha = 0.1$ level; however, the outcome variable is highly positively skewed.

@@

We conclude using paired comparisons that customers who had SEED accounts saw an increase in savings over the duration of the trial. We conclude using Tukey Permutation Honest Significant Difference tests that SEED accounts had more savings than the other two groups. Finally, using M-Estimation and rank-based and robust regression we find that SEED accounts had more savings than the other two groups; however, we find much smaller effect sizes than [@Ashraf2006].

Section 2 describes and summarizes the analysis data. In section 3, we test the effectiveness of the SEED accounts on overall savings. In section 4, we test the effectiveness of the SEED accounts against the control group and the marketing treatment. In section 5, use use robust regression techniques to estimate linear regression models that are more appropriate in the presence of outliers.

@@

```{r}
#
# Create a histogram to show the skew of balchange
#
skewa = six_months %>%
  ggplot(aes(balchange)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(limits = c(0, 2000),
                     labels = scales::comma) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal()

skewb = treated %>%
  ggplot(aes(balchange)) +
  geom_histogram() +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(limits = c(0, 2000),
                     labels = scales::comma) +
  labs(title = "",
       subtitle = "Twelve Month Change in Balance",
       x = "Change in balance (Philippine Peso)",
       y = NULL) +  
  theme_minimal()

Here is the same information as a kernel density estimate (KDE).

```{r}
#
# Create a density plot to show the skew of balchange
#
skewa = six_months %>%
  ggplot(aes(balchange)) +
  geom_density() +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(limits = c(0, 0.004)) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal()

@@

```{r}
seed_accounts = treated %>% 
  filter(treatment == 1)
nonseed = treated %>% 
  filter(treatment == 0)
